---
title: "Developing Data Products Project"
author: "Luis Andre Dutra e Silva"
date: "3/29/2018"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(plotly)
library(shiny)
library(shinyBS)
```

## Summary

This Shiny project renders an interactive 3D scattered graph using Plotly. All datasets are available to the user in order to choose the axis on the fly.

- Interface is completely reactive
- Popovers are available to explain each element


## Example Code

- The following code retrives the second dataset in the list of R default datasets: 
```{r cars, echo = TRUE}
names <- names(data())
res <- data()$results
res <- data.frame(res)
res <- res[res$Package=="datasets",]
res <- res[order(res$Item),]
datasets <- res$Item
name <- as.character(datasets[1])
data(list=name)
eval(parse(text=paste("dataset <- ",name)))
ds <- data.frame(dataset)
ds
```

## Slide with Plot

- The folowing chart is rendered with the previous dataset
```{r pressure}

p <- plot_ly(ds, x = ~cov.general, y = ~cov.picture, z = ~cov.blocks, color =~cov.maze, colors = c('#BF382A', '#0C4B8E')) %>%
                    add_markers() %>%
                    layout(scene = list(xaxis = list(title = "cov.general"),
                                        yaxis = list(title = "cov.picture"),
                                        zaxis = list(title = "cov.blocks")))
p
```

## Conclusion

The tools used in this course are very useful for the purpose of distributing the result of a data analysis research project. I think that the professionalism of each tool is what sets this specialization apart.
